---
title: "Analysis of the basic data"
author: "Claire Chu"
date: "July 20, 2016"
output: 
  html_document:
    keep_md: yes
---

###2.0 Analysis of the basic data

---2.1 [Development of the business portfolio](#id-section2.1)

---2.2 [Correlation between As Is and Plan data](#id-section2.2)

---2.3 [Time series analysis](#id-section2.3)

-------2.3.1 ["stl" function](#id-section2.3.1)

-------2.3.2 [Modification of the seasonal componant to a monthly base](#id-section2.3.2)

<br>

****************************
######Load the following libraries and packages.
```{r echo=TRUE, message=FALSE}
setwd("/Users/macnificent/Desktop")
library(fpp)
library(tcltk)

mywait <- function() {
    tt <- tktoplevel()
    tkpack( tkbutton(tt, text='Continue', command=function()tkdestroy(tt)),
        side='bottom')
    tkbind(tt,'<Key>', function()tkdestroy(tt) )

    tkwait.window(tt)
}

#Section 1 Code required to complete the code below
ImportedAsIsData <- read.csv("ImportedAsIsDataChulwalar.csv", header = F, sep=";", fill = T)
ImportedPlanData <- read.csv("ImportedPlanDataChulwalar.csv", header = F, sep=";", fill = T)
ImportedIndicators <- read.csv("ImportedIndicatorsChulwalar.csv", header = F, sep=";", fill = T)
TotalAsIsVector <- c(ImportedAsIsData [2:13,2],ImportedAsIsData [2:13,3],ImportedAsIsData [2:13,4],ImportedAsIsData [2:13,5],ImportedAsIsData [2:13,6],ImportedAsIsData [2:13,7])
EfakAsIsVector <- c(ImportedAsIsData [16:27,2],ImportedAsIsData [16:27,3],ImportedAsIsData [16:27,4],ImportedAsIsData [16:27,5],ImportedAsIsData [16:27,6],ImportedAsIsData [16:27,7])
WugeAsIsVector <- c(ImportedAsIsData [30:41,2],ImportedAsIsData [30:41,3],ImportedAsIsData [30:41,4],ImportedAsIsData [30:41,5],ImportedAsIsData [30:41,6],ImportedAsIsData [30:41,7])
TotalEtelAsIsVector <- c(ImportedAsIsData [44:55,2],ImportedAsIsData [44:55,3],ImportedAsIsData [44:55,4],ImportedAsIsData [44:55,5],ImportedAsIsData [44:55,6],ImportedAsIsData [44:55,7])
BlueEtelAsIsVector <- c(ImportedAsIsData [58:69,2],ImportedAsIsData [58:69,3],ImportedAsIsData [58:69,4],ImportedAsIsData [58:69,5],ImportedAsIsData [58:69,6],ImportedAsIsData [58:69,7])
RedEtelAsIsVector <- c(ImportedAsIsData [72:83,2],ImportedAsIsData [72:83,3],ImportedAsIsData [72:83,4],ImportedAsIsData [72:83,5],ImportedAsIsData [72:83,6],ImportedAsIsData [72:83,7])
YearAsIsVector <- c(ImportedAsIsData [86,2],ImportedAsIsData [86,3],ImportedAsIsData [86,4],ImportedAsIsData [86,5],ImportedAsIsData [86,6],ImportedAsIsData [86,7])
TotalAsIsVector_2014 <- c(ImportedAsIsData[2:13,8])
TotalAsIs<- ts(TotalAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakAsIs <- ts(EfakAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
WugeAsIs <- ts(WugeAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelAsIs<- ts(TotalEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelAsIs <- ts(BlueEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelAsIs <- ts(RedEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearAsIs <- ts(YearAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalAsIs_2014 <- ts(TotalAsIsVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)
PlanVector <- c(ImportedPlanData[2:13,2],ImportedPlanData[2:13,3],ImportedPlanData[2:13,4],ImportedPlanData[2:13,5],ImportedPlanData[2:13,6],ImportedPlanData[2:13,7])
EfakPlanVector <- c(ImportedPlanData[16:27,2],ImportedPlanData[16:27,3],ImportedPlanData[16:27,4],ImportedPlanData[16:27,5],ImportedPlanData[16:27,6],ImportedPlanData[16:27,7])
WugePlanVector <- c(ImportedPlanData[30:41,2],ImportedPlanData[30:41,3],ImportedPlanData[30:41,4],ImportedPlanData[30:41,5],ImportedPlanData[30:41,6],ImportedPlanData[30:41,7])
TotalEtelPlanVector <- c(ImportedPlanData[44:55,2],ImportedPlanData[44:55,3],ImportedPlanData[44:55,4],ImportedPlanData[44:55,5],ImportedPlanData[44:55,6],ImportedPlanData[44:55,7])
BlueEtelPlanVector <- c(ImportedPlanData[58:69,2],ImportedPlanData[58:69,3],ImportedPlanData[58:69,4],ImportedPlanData[58:69,5],ImportedPlanData[58:69,6],ImportedPlanData[58:69,7])
RedEtelPlanVector <- c(ImportedPlanData[72:83,2],ImportedPlanData[72:83,3],ImportedPlanData[72:83,4],ImportedPlanData[72:83,5],ImportedPlanData[72:83,6],ImportedPlanData[72:83,7])
YearPlanVector <- c(ImportedPlanData[86,2],ImportedPlanData[86,3],ImportedPlanData[86,4],ImportedPlanData[86,5],ImportedPlanData[86,6],ImportedPlanData[86,7])
PlanVector_2014 <- c(ImportedPlanData[2:13,8])
TotalPlan <- ts(PlanVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakPlan <- ts(EfakPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
WugePlan <- ts(WugePlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelPlan <- ts(TotalEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelPlan <- ts(BlueEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelPlan <- ts(RedEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearPlan <- ts(YearPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalPlan_2014 <- ts(PlanVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)
```

****************************
<div id='id-section2.1'/>
####2.1 Development of the business portfolio

#####Due to the different scales, it makes sense to plot each graph individually instead of plotting them all on one set of axes. 
```{r}
par(mfrow=c(3,2))

plot(TotalAsIs, col="black", main="TotalAsIs")
plot(EfakAsIs , col="red",main="EfakAsIs")
plot(WugeAsIs, col="blue", main="WugeAsIs")
plot(TotalEtelAsIs, col="green",main="TotalEtelAsIs")
plot(BlueEtelAsIs, col="orange", main="BlueEtelAsIs")
plot(RedEtelAsIs, col="purple", main="RedEtelAsIs")

mywait()
```
#####These 6 graphs plot the data for the various As Is variables
```{r}
mywait()
par(mfrow=c(3,2))

plot(TotalPlan , col="black", main="TotalPlan")
plot(EfakPlan , col="red",main="EfakPlan")
plot(WugePlan, col="blue", main="WugePlan")
plot(TotalEtelPlan, col="green",main="TotalEtelPlan")
plot(BlueEtelPlan, col="orange", main="BlueEtelPlan")
plot(RedEtelPlan, col="purple", main="RedEtelPlan")

mywait()
```
#####These 6 graphs plot the data for the various Plan variables

****************************
<div id='id-section2.2'/>
####2.2 Correlation between As Is and Plan data

##### Test the correlation between As Is and Plan data in order to test how exact the planning is. Correlation is a measure of linear relationship between two variables. 
```{r}
cor(TotalAsIs, TotalPlan )
cor(EfakAsIs , EfakPlan)
cor(WugeAsIs, WugePlan)
cor(TotalEtelAsIs, TotalEtelPlan)
cor(BlueEtelAsIs , BlueEtelPlan)
cor(RedEtelAsIs , RedEtelPlan)
cor(YearAsIs, YearPlan)

mywait()
```
#####The results show a very high planning accuracy since all the correlation coefficients are close to 1. 

```{r}
TotalAsIs_lm <- lm(TotalAsIs ~ TotalPlan , data = TotalAsIs)
summary(TotalAsIs_lm)

TotalAsIs_tslm <- tslm(TotalAsIs ~ TotalPlan )
summary(TotalAsIs_tslm)
```
#####Running a regression model on the Total As Is time series to compare the Total As Is data time series, we can see that the R-squared is 00.84 so our model is a good fit for linear regression

****************************
<div id='id-section2.3'/>
####2.3 Time series analysis

****************************
<div id='id-section2.3'/>
####2.3.1 "stl" function 
#####The time series can be analysed using the stl function in order to seperate the trend, seasonality and remainder (remaining coincidential) components from one another.

```{r}
TotalAsIs_stl <- stl(TotalAsIs, s.window=5)
EfakAsIs_stl <- stl(EfakAsIs , s.window=5)
WugeAsIs_stl <- stl(WugeAsIs, s.window=5)
TotalEtelAsIs_stl <- stl(TotalEtelAsIs, s.window=5)
BlueEtelAsIs_stl <- stl(BlueEtelAsIs , s.window=5)
RedEtelAsIs_stl <- stl(RedEtelAsIs , s.window=5)
```

#####Thus the individual time series can be shown graphically and tabularly. The trend of the total exports is almost linear. A relatively uniform seasonality can be seen.
```{r}
par(mfrow=c(3,2))

plot(TotalAsIs_stl, col="black", main="TotalAsIs_stl")
TotalAsIs_stl
```
######It is interesting to note that the almost linear trend is not seen in the individual segments. The individual trends run partially in opposite directions in the middle of the time scale, which causes the linear trend in the total As Is data.
```{r}

plot(EfakAsIs_stl, col="black", main="EfakAsIs_stl")
EfakAsIs_stl

plot(WugeAsIs_stl, col="black", main="WugeAsIs_stl")
WugeAsIs_stl

plot(TotalEtelAsIs_stl, col="black", main="TotalEtelAsIs_stl")
TotalEtelAsIs_stl

plot(BlueEtelAsIs_stl, col="black", main="BlueEtelAsIs_stl")
BlueEtelAsIs_stl

plot(RedEtelAsIs_stl, col="black", main="RedEtelAsIs_stl")
RedEtelAsIs_stl

mywait()
```

```{r}
par(mfrow=c(3,2))

plot(TotalAsIs_stl$time.series[,"trend"], col="black")
plot(EfakAsIs_stl$time.series[,"trend"], col="red")
plot(WugeAsIs_stl$time.series[,"trend"], col="blue")
plot(TotalEtelAsIs_stl$time.series[,"trend"], col="green")
plot(BlueEtelAsIs_stl$time.series[,"trend"], col="orange")
plot(RedEtelAsIs_stl$time.series[,"trend"], col="purple")

mywait()
```

****************************
<div id='id-section2.3.2'/>
####2.3.2 Modification of the seasonal componant to a monthly base

##### The modification of the seasonlity component can also be changed into a monthly view. It only makes sense to do this if the seasonality componant as the trend looks almost identical and the remainder is then randomly spread.
```{r}

monthplot(TotalAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
monthplot(EfakAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
monthplot(WugeAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
monthplot(TotalEtelAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
monthplot(BlueEtelAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
monthplot(RedEtelAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")

mywait()
```
