---
title: "Preperation, import and convert data"
author: "Claire Chu"
date: "July 20, 2016"
output: 
  html_document:
    keep_md: yes
---

###1.0 Preperation, import and convert data for Chulwalar Exports

---1.1 [Import the exports data and the indicators](#id-section1.1)

---1.2 [Transforming the data into vectors and time series](#id-section1.2)

<br>

****************************
######Load the following libraries and packages.
```{r echo=TRUE, message=FALSE}
setwd("/Users/macnificent/Desktop")
library(fpp)
library(tcltk)

source('~/Desktop/mywait.r')
```

****************************
<div id='id-section1.1'/>
####1.1 Import the exports data and the indicators

```{r}
ImportedAsIsData <- read.csv("ImportedAsIsDataChulwalar.csv", header = F, sep=";", fill = T)

ImportedPlanData <- read.csv("ImportedPlanDataChulwalar.csv", header = F, sep=";", fill = T)

ImportedIndicators <- read.csv("ImportedIndicatorsChulwalar.csv", header = F, sep=";", fill = T)

head(ImportedAsIsData)
head(ImportedPlanData)
head(ImportedIndicators)
```

######The data provided comprises of the following partial data sets:
IMPORTED AS IS DATA

-Monthly As Is exports 

-Monthly As Is exports of Efak

-Monthly As Is exports of Wuge

-Monthly As Is exports of Etel (Total)

-Monthly As Is exports of blue Etel

-Monthly As Is exports of red Etel

-Yearly As Is exports


IMPORTED PLAN DATA

-Monthly Plan exports 

-Monthly Plan exports of Efak

-Monthly Plan exports of Wuge

-Monthly Plan exports of Etel (Total)

-Monthly Plan exports of blue Etel

-Monthly Plan exports of red Etel

-Yearly Plan exports



IMPORTED INDICATORS

-Change in Exports prices

-Satisfaction index

-Average Temperature

-Birth Index

-Satisfaction index (Independent)

-Total Exports from Urbano

-Globalization Party Members

-Average Export Price

-Etel Production Price index

-Chulwalar Index

-Inflation

-Spending for Chulwalar holidays

-Chulwalar holidays

-Influence of Chulwalar holidays

****************************
<div id='id-section1.2'/>
####1.2 Transforming the data into vectors and time series 
#####We need to separate the data so that we can do partial dataset analysis on each time series
#####Seperating the Imported As Is Data
```{r}
TotalAsIsVector <- c(ImportedAsIsData [2:13,2],ImportedAsIsData [2:13,3],ImportedAsIsData [2:13,4],ImportedAsIsData [2:13,5],ImportedAsIsData [2:13,6],ImportedAsIsData [2:13,7])
EfakAsIsVector <- c(ImportedAsIsData [16:27,2],ImportedAsIsData [16:27,3],ImportedAsIsData [16:27,4],ImportedAsIsData [16:27,5],ImportedAsIsData [16:27,6],ImportedAsIsData [16:27,7])
WugeAsIsVector <- c(ImportedAsIsData [30:41,2],ImportedAsIsData [30:41,3],ImportedAsIsData [30:41,4],ImportedAsIsData [30:41,5],ImportedAsIsData [30:41,6],ImportedAsIsData [30:41,7])
TotalEtelAsIsVector <- c(ImportedAsIsData [44:55,2],ImportedAsIsData [44:55,3],ImportedAsIsData [44:55,4],ImportedAsIsData [44:55,5],ImportedAsIsData [44:55,6],ImportedAsIsData [44:55,7])
BlueEtelAsIsVector <- c(ImportedAsIsData [58:69,2],ImportedAsIsData [58:69,3],ImportedAsIsData [58:69,4],ImportedAsIsData [58:69,5],ImportedAsIsData [58:69,6],ImportedAsIsData [58:69,7])
RedEtelAsIsVector <- c(ImportedAsIsData [72:83,2],ImportedAsIsData [72:83,3],ImportedAsIsData [72:83,4],ImportedAsIsData [72:83,5],ImportedAsIsData [72:83,6],ImportedAsIsData [72:83,7])
YearAsIsVector <- c(ImportedAsIsData [86,2],ImportedAsIsData [86,3],ImportedAsIsData [86,4],ImportedAsIsData [86,5],ImportedAsIsData [86,6],ImportedAsIsData [86,7])
TotalAsIsVector_2014 <- c(ImportedAsIsData[2:13,8])
```
#####Converting the Imported As Is vectors into a time series
```{r}
TotalAsIs<- ts(TotalAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakAsIs <- ts(EfakAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
WugeAsIs <- ts(WugeAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelAsIs<- ts(TotalEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelAsIs <- ts(BlueEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelAsIs <- ts(RedEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearAsIs <- ts(YearAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalAsIs_2014 <- ts(TotalAsIsVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)
```

#####Separating the Imported Plan Data
```{r}
PlanVector <- c(ImportedPlanData[2:13,2],ImportedPlanData[2:13,3],ImportedPlanData[2:13,4],ImportedPlanData[2:13,5],ImportedPlanData[2:13,6],ImportedPlanData[2:13,7])
EfakPlanVector <- c(ImportedPlanData[16:27,2],ImportedPlanData[16:27,3],ImportedPlanData[16:27,4],ImportedPlanData[16:27,5],ImportedPlanData[16:27,6],ImportedPlanData[16:27,7])
WugePlanVector <- c(ImportedPlanData[30:41,2],ImportedPlanData[30:41,3],ImportedPlanData[30:41,4],ImportedPlanData[30:41,5],ImportedPlanData[30:41,6],ImportedPlanData[30:41,7])
TotalEtelPlanVector <- c(ImportedPlanData[44:55,2],ImportedPlanData[44:55,3],ImportedPlanData[44:55,4],ImportedPlanData[44:55,5],ImportedPlanData[44:55,6],ImportedPlanData[44:55,7])
BlueEtelPlanVector <- c(ImportedPlanData[58:69,2],ImportedPlanData[58:69,3],ImportedPlanData[58:69,4],ImportedPlanData[58:69,5],ImportedPlanData[58:69,6],ImportedPlanData[58:69,7])
RedEtelPlanVector <- c(ImportedPlanData[72:83,2],ImportedPlanData[72:83,3],ImportedPlanData[72:83,4],ImportedPlanData[72:83,5],ImportedPlanData[72:83,6],ImportedPlanData[72:83,7])
YearPlanVector <- c(ImportedPlanData[86,2],ImportedPlanData[86,3],ImportedPlanData[86,4],ImportedPlanData[86,5],ImportedPlanData[86,6],ImportedPlanData[86,7])
PlanVector_2014 <- c(ImportedPlanData[2:13,8])
```
#####Converting the Imported Plan Vectors into a time series
```{r}
TotalPlan <- ts(PlanVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakPlan <- ts(EfakPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
WugePlan <- ts(WugePlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelPlan <- ts(TotalEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelPlan <- ts(BlueEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelPlan <- ts(RedEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearPlan <- ts(YearPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalPlan_2014 <- ts(PlanVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)
```

##### Call up the As Is time series to check everything has worked.
```{r}
TotalAsIs
EfakAsIs
WugeAsIs
TotalEtelAsIs
BlueEtelAsIs 
RedEtelAsIs 
YearAsIs
TotalAsIs_2014
```
##### Call up the Plan time series to check everything has worked.
```{r}
TotalPlan
EfakPlan
WugePlan 
TotalEtelPlan
BlueEtelPlan
RedEtelPlan
YearPlan
TotalPlan_2014
```
